Poster Analysis

### 2024-10-24 Manuscript Analysis/ASHA Poster Analyses.Rmd
updated peak pupil analysis

m2 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + (trial_c|subject), data = peak_pupil_df)
sjPlot::tab_model(m2, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m1, m2)

@@

m3 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + scale(list_sort_c, scale = F) + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m3, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m2, m3)

@@

m3b <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m3b, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m3, m3b)

@@

m4 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + scale(flanker_c, scale = F) + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m4, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m3b, m4)

@@

m5 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + scale(card_sort_c, scale = F) + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m5, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m3b, m5)

@@

m6 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + scale(pattern_c,scale = F) + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m6, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m3b, m6)

@@

m7 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                speaker*scale(list_sort_c, scale = F) + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m7, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m3b, m7)

@@

m8 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                speaker*scale(list_sort_c, scale = F) + speaker*scale(flanker_c, scale = F) + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m8, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m7, m8)

@@

m9 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m9, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m7, m9)

@@

m10 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + speaker*scale(pattern_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m10, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m9, m10)

@@

m11 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m11, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m9, m11)

@@

m12 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) + rep_acc*scale(flanker_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m12, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m11, m12)

@@

m13 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) + rep_acc*scale(card_sort_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m13, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m11, m13)

@@

m14 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) + rep_acc*scale(pattern_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m14, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m11, m14)

@@

m15 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) + rep_acc*scale(pattern_c, scale = F) +
                 speaker*rep_acc*scale(list_sort_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m15, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m14, m15)

@@

m16 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) + rep_acc*scale(pattern_c, scale = F) +
                 speaker*rep_acc*scale(flanker_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m16, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m14, m16)

@@

m17 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) + rep_acc*scale(pattern_c, scale = F) +
                 speaker*rep_acc*scale(card_sort_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m17, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m14, m17)

@@

m18 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) + rep_acc*scale(pattern_c, scale = F) +
                 speaker*rep_acc*scale(pattern_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m18, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m14, m18)

@@

### Best-Fitting Final Model

@@

m14b <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                  speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                  rep_acc*scale(pattern_c, scale = F) +
                  (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m14b, pred.labels = "Intercept",
                  dv.labels = "Peak Pupil Dilation")
performance::check_model(m14b)
performance::test_performance(m14, m14b)

>>>>

m2 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + (trial_c|subject), data = peak_pupil_df)
sjPlot::tab_model(m2, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Speaker * Repetition Accuracy"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m1, m2)

@@

m3 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + scale(list_sort_c, scale = F) + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m3, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Speaker * Repetition Accuracy"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m2, m3)

@@

m3b <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m3b,
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]", 
                                  "Speaker * Repetition Accuracy"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m3, m3b)

@@

m4 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + scale(flanker_c, scale = F) + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m4, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Inhibitory Control", "Speaker * Repetition Accuracy"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m3b, m4)

@@

m5 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + scale(card_sort_c, scale = F) + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m5, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Cognitive Flexibility", "Speaker * Repetition Accuracy"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m3b, m5)

@@

m6 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + scale(pattern_c,scale = F) + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m6, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Processing Speed", "Speaker * Repetition Accuracy"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m3b, m6)

@@

m7 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                speaker*scale(list_sort_c, scale = F) + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m7, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Speaker * Repetition Accuracy", "Working Memory * Speaker [ALS]"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m3b, m7)

@@

m8 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                speaker*scale(list_sort_c, scale = F) + speaker*scale(flanker_c, scale = F) + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m8, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Inhibitory Control", 
                                  "Speaker * Repetition Accuracy", "Working Memory * Speaker [ALS]",
                                  "Inhibitory Control * Speaker [ALS]"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m7, m8)

@@

m9 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m9, 
                   pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Cognitive Flexibility",
                                  "Speaker * Repetition Accuracy", "Working Memory * Speaker [ALS]",
                                  "Cognitive Flexibility * Speaker [ALS]"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m7, m9)

@@

m10 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + speaker*scale(pattern_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m10, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Cognitive Flexibility", "Processing Speed",
                                  "Speaker * Repetition Accuracy", "Working Memory * Speaker [ALS]",
                                  "Cognitive Flexibility * Speaker [ALS]", "Processing Speed * Speaker [ALS]"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m9, m10)

@@

m11 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m11, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Cognitive Flexibility", 
                                  "Speaker * Repetition Accuracy", "Working Memory * Speaker [ALS]",
                                  "Cognitive Flexibility * Speaker [ALS]", 
                                  "Working Memory * Accuracy [Inaccuraate]"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m9, m11)

@@

m12 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) + rep_acc*scale(flanker_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m12, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Cognitive Flexibility", "Inhibitory Control",
                                  "Speaker * Repetition Accuracy", "Working Memory * Speaker [ALS]",
                                  "Cognitive Flexibility * Speaker [ALS]", 
                                  "Working Memory * Accuracy [Inaccurate]",
                                  "Inhibitory Control * Accuracy [Inaccurate]"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m11, m12)

@@

m13 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) + rep_acc*scale(card_sort_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m13, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Cognitive Flexibility",
                                  "Speaker * Repetition Accuracy", "Working Memory * Speaker [ALS]",
                                  "Cognitive Flexibility * Speaker [ALS]", 
                                  "Working Memory * Accuracy [Inaccurate]",
                                  "Cognitive Flexibility * Accuracy [Inaccurate]"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m11, m13)

@@

m14 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) + rep_acc*scale(pattern_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m14, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Cognitive Flexibility", "Processing Speed",
                                  "Speaker * Repetition Accuracy", "Working Memory * Speaker [ALS]",
                                  "Cognitive Flexibility * Speaker [ALS]", 
                                  "Working Memory * Accuracy [Inaccurate]",
                                  "Processing Speed * Accuracy [Inaccurate]"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m11, m14)

@@

m15 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) + rep_acc*scale(pattern_c, scale = F) +
                 speaker*rep_acc*scale(list_sort_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m15, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Cognitive Flexibility", "Processing Speed",
                                  "Speaker * Repetition Accuracy", "Working Memory * Speaker [ALS]",
                                  "Cognitive Flexibility * Speaker [ALS]", 
                                  "Working Memory * Accuracy [Inaccurate]",
                                  "Processing Speed * Accuracy [Inaccurate]",
                                  "Working Memory * Speaker * Accuracy"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m14, m15)

@@

m16 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) + rep_acc*scale(pattern_c, scale = F) +
                 speaker*rep_acc*scale(flanker_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m16, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Cognitive Flexibility", "Processing Speed", "Inhibitory Control",
                                  "Speaker * Repetition Accuracy", "Working Memory * Speaker [ALS]",
                                  "Cognitive Flexibility * Speaker [ALS]", 
                                  "Working Memory * Accuracy [Inaccurate]",
                                  "Processing Speed * Accuracy [Inaccurate]",
                                  "Inhibitory Control * Speaker [ALS]",
                                  "Inhibitory Control * Accuracy [Inaccurate]",
                                  "Inhibitory Control * Speaker * Accuracy"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m14, m16)

@@

m17 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) + rep_acc*scale(pattern_c, scale = F) +
                 speaker*rep_acc*scale(card_sort_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m17, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Cognitive Flexibility", "Processing Speed",
                                  "Speaker * Repetition Accuracy", "Working Memory * Speaker [ALS]",
                                  "Cognitive Flexibility * Speaker [ALS]", 
                                  "Working Memory * Accuracy [Inaccurate]",
                                  "Processing Speed * Accuracy [Inaccurate]",
                                  "Cognitive Flexibility * Accuracy [Inaccurate]",
                                  "Cognitive Flexibility * Speaker * Accuracy"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m14, m17)

@@

m18 <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                 speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                 rep_acc*scale(list_sort_c, scale = F) + rep_acc*scale(pattern_c, scale = F) +
                 speaker*rep_acc*scale(pattern_c, scale = F) +
                 (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m18, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Cognitive Flexibility", "Processing Speed",
                                  "Speaker * Repetition Accuracy", "Working Memory * Speaker [ALS]",
                                  "Cognitive Flexibility * Speaker [ALS]", 
                                  "Working Memory * Accuracy [Inaccurate]",
                                  "Processing Speed * Accuracy [Inaccurate]",
                                  "Processing Speed * Speaker [ALS]",
                                  "Processing Speed * Speaker * Accuracy"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m14, m18)

@@

### Removing the interaction between repetition accuracy and working memory

@@

m14b <- glmmTMB(peak_pupil ~ trial_c + speaker*rep_acc + 
                  speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                  rep_acc*scale(pattern_c, scale = F) +
                  (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m14b, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Cognitive Flexibility", "Processing Speed", 
                                  "Speaker * Repetition Accuracy", "Working Memory * Speaker [ALS]",
                                  "Cognitive Flexibility * Speaker [ALS]",
                                  "Processing Speed * Repetition Accuracy [Inacccurate]"),
                  dv.labels = "Peak Pupil Dilation")
performance::test_performance(m14, m14b)

### Best Fitting Final Model

m14c <- glmmTMB(peak_pupil ~ trial_c + speaker + rep_acc + 
                  speaker*scale(list_sort_c, scale = F) + speaker*scale(card_sort_c, scale = F) + 
                  rep_acc*scale(pattern_c, scale = F) +
                  (1|subject), data = peak_pupil_df)
sjPlot::tab_model(m14c, 
                  pred.labels = c("Intercept", "Trial Number", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Working Memory", "Cognitive Flexibility", "Processing Speed", 
                                  "Working Memory * Speaker [ALS]",
                                  "Cognitive Flexibility * Speaker [ALS]", 
                                  "Processing Speed * Repetition Accuracy [Inacccurate]"),
                  dv.labels = "Peak Pupil Dilation",
                  show.std = T,
                  file = "Tables/Peak_pupil_model.html")
performance::check_model(m14c)
performance::test_performance(m14b, m14c)
